\documentclass[10pt,a4paper]{report}
\author{Kyle Lemons}
\title{Halo3 Game Master User's Guide \\
{\large{Current Version: Halo3-v0.1.3}}}
\begin{document}
\maketitle
\tableofcontents
\pagebreak

\chapter{Introduction}
First off, thank you for downloading this package!  I hope you find it as useful as we have.
There are some basic things about the motivations for why this was created that might make use of it easier:
\begin{enumerate}
\item We have frequent, well-attended events at which Halo is the central theme.
\item Fairness, speed, and variety are key components in these events.
\item There are typically any number of Xboxes on the premises, each devoted to a particular team.
\item It is not practical for everybody to crowd around one computer screen to find where their teams are.
\item Multiple computers should be able to reliably show the same game state, and updates should be very fast.
\item To keep things flowing, there needs to be some visible indication of how much time remains before the game begins.
\item To accomodate different skill levels of players, games should be generated such that they are not consistently ganged up upon.
\item The system should be as self-sufficient as possible.
\item All of these basically add up to one thing: Maximize the amount of fun that can be had in any given amount of time!
\end{enumerate}

\chapter{Keys and Commands}
\section{Game Screen}
\begin{tabular}{c|c|l}
Fn Key & Hot Key & Command \\
\hline
F2 & P & Switch to the Player Editor \\
F3 & G & Switch to the Game/Map Editor \\
F4 & S & Switch to the Setup Editor \\
F5 & R & Hold for 4 seconds to regenerate the Game \\
\end{tabular}

\section{Player Editor}
\begin{tabular}{c|c|l}
Fn Key & Hot Key & Command \\
\hline
& Space & Toggle the "Is Playing?" status of active player \\
F1 & & Switch back to the Main Screen \\
F3 & & Switch to the Game/Map Editor \\
F4 & & Switch to the Setup Editor \\
\end{tabular}
\\
\\
Note that the Space hot key only works when you have the player selected in the list, e.g. immediately after clicking on the player.  If another input has focus, this hot key will not work.  This is intended for quickly adjusting the active players by using the arrow keys and the space bar in the user list.

\section{Game and Map Editor}
\begin{tabular}{c|c|l}
Fn Key & Hot Key & Command \\
\hline
F1 & & Switch back to the Main Screen \\
F3 & & Switch to the Game/Map Editor \\
F4 & & Switch to the Setup Editor \\
\end{tabular}

\section{Settings Editor}
\begin{tabular}{c|c|l}
Fn Key & Hot Key & Command \\
\hline
F1 & & Switch back to the Main Screen \\
F3 & & Switch to the Game/Map Editor \\
F4 & & Switch to the Setup Editor \\
\end{tabular}

\end{document}
